---
title: "Logistic Regression Modeling"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# 1:Introduction
In the recent past, minorities in Tacoma, Washington were denied access to home loans based on where they lived. This practice is known as redlining because property assessors would create maps with minority communities outlined in red. The red outline told bankers those minority communities were not fit for loans. The consequence of redlining was a significant disparity in mortgage loans and homeownership rates between white communities and minority communities.

Today, banks don’t practice redlining, but disparities in mortgage loans and homeownership still exist at a significant rate. For example, the average homeownership rate in the West Census Region is 59.3 %; however, the average homeownership rate for minorities (47.9 %) is 11.4 points below the West Census Region's average, and 25.2 points below their white peers (73.1 %).

Homeownership is an effective wealth generating tool. According to a study conducted by the Demos organization, if disparites in homeownership rates were closed; the wealth gap between white and black families decreased by 31 %. Because of these circumstances, an analysis of home mortgage data to discover patterns in loan approval / denial rates in the Tacoma-Lakewwood area is warranted.


## 1.1: Data
Analysis began by gathering data from the Consumer Financial Protection Bureau (CFPB). The CFPB provides access to loan-level data so that trends in mortgage applications can be monitored. Action taken on loan applications, HUD median income, loan amount, appliancts income, race and ethnicity, gender, loan type and purpose are some of the variables that are included in the dataset from the CFPB. For this analyses, the mortgage dataset included 35,000 observations for the Tacoma-Lakewood area, of which 85 % of the applicants were approved for mortgages. 

## 1.2: Methods
To guide the modeling approach, the process began with the assumption that minorities were denied mortgage loans at a greater rate than non-minorites when controlling for loan amount,income and other factors. This hypothesis was based on trends in homeownership rates. Furthermore, logistic regression was used to generate the probability of the rejection of a mortgage loan based on race.

# 2: Exploratory Analysis
Exploratory analysis was used to understand how categorical variables were related and the associations between continuous, independent variables.

## 2:1 Exploratory Analysis of Categorical Variables

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the sam place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation =1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag), from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You learn all of these things and more can be customized in each R code block.

# The big idea

Use this lab journal to record what you do in R. This way I will be able to see what you are doing and help you along the way. You will also be creating a repository of all the things you do. You can make posts about everything. Learning specific things in R (project unrelated), and doing things for the project that we will discuss at the beginning of the Fall semester. You can get started now by fiddling around with googling things, and trying stuff out in R. I've placed some helpful starting links in the links page on this website

# What can you do right now by yourself?

It's hard to learn programming when you don't have specific problems that you are trying to solve. Everything just seems abstract.

I wrote an [introductory programming book that introduces R](https://crumplab.github.io/programmingforpsych/), and gives some [concrete problems for you to solve](https://crumplab.github.io/programmingforpsych/programming-challenges-i-learning-the-fundamentals.html). 

To get the hang of journaling and solving the problems to learn programming, my suggestion is that you use this .Rmd file to solve the problems. It would look like this:

# Problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+2
2*5
5/3
(1+6+4)/5

```

# Problem 2

Put numbers into variables, do simple math on the variables

```{r}
a<-1
b<-2
a+b

d<-c(1,2,3)
e<-c(5,6,7)
d+e
d*e
d/e

```

# Problem 3

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
# for loop solution
# i becomes the number 1 to 100 at each step of the loop


a <- length(100) # make empty variable, set length to 100
for (i in 1:100){
  a[i] <-i #assigns the number in i, to the ith index of a
}

print(a)

# for loop solution #2

a<-c() #create empty variable using combine command
for (i in 1:100){
  a<-c(a,i) # keeps combining a with itself and the new number in i
}
print(a)

# seq solution
a <- seq(1,100,1) # look up help for seq using ?seq() in console
print(a)

```

# Replace this with problem 4

And keep going. Try to solve the problems with different scripts that provide the same solution. Good luck, Happy coding.
